---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [Student name]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# demographics
data_demographics_raw <- read_csv("../data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# data_demographics_raw_messy <- read_csv("../data/raw/data_demographics_raw_messy.csv", skip = 2) |>
#   janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../data/raw/data_selfreport_raw.csv") |>
  janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```

# Demographics

```{r}

dat_age_gender <- data_demographics_raw |>
  select(subject, date, time, trialcode, response) |>
  pivot_wider(names_from = trialcode,
              values_from = response) |>
  mutate(gender = tolower(gender),
         gender = stringr::str_remove_all(gender, regex("\\W+")), # regex is both very useful and awful to write
         gender = case_when(gender == "female" ~ gender,
                            gender == "male" ~ gender,
                            gender == "nonbinary" ~ gender,
                            gender == "woman" ~ "female",
                            gender == "man" ~ "male",
                            TRUE ~ "other/missing/error"),
         age = case_when(str_detect(age, "^[0-9]+$") ~ age, # if the value is only numbers, keep it. 
                         TRUE ~ "other/missing/error")) 

```

# Exclusions / data quality

## AMP

```{r}

data_amp_performance_criteria <- data_amp_raw |> 
  filter(blockcode != "practice", 
         trialcode != "instructions") |> 
  mutate(latency_prob = if_else(latency < 100, TRUE, FALSE)) |> 
  group_by(subject) |> 
  summarize(proportion_fast_trials_amp = mean(latency_prob)) |>
  mutate(exclude_amp_performance = ifelse(proportion_fast_trials_amp > 0.10, "exclude", "include"))

# determine modal number of trials
data_amp_completeness <- data_amp_raw |>
  filter(blockcode != "practice",
         trialcode != "instructions") |>
  group_by(subject) |>
  count() |>
  ungroup() |>
  mutate(exclude_amp_completeness = ifelse(n == 72, "include", "exclude")) |>
  select(-n)

# data_amp_completeness |>
#   count(n)

```

- One participant with 8 trials appears to be a partial completion (check raw data?)
- One participant with 144 trials appears to be a repeat participant. I've chosen to exclude them entirely, but you could also have a more elaborate strategy where you retain only their first completion.

# Assignment 8
```{r}
data_amp_prime_target <- data_amp_raw |>
  select("subject", blockcode, "trialcode", "primestim", "targetstim", evaluative_response = correct) |>
  filter(blockcode != "practice",
         trialcode != "instructions") |>
mutate(is_congruent = case_when(trialcode == "prime_positive" & evaluative_response == 1 ~ TRUE, 
                                  trialcode == "prime_negative" & evaluative_response == 0 ~ TRUE, 
                                  TRUE ~ FALSE))

view(data_amp_prime_target)


data_amp_with_amp_score <- data_amp_prime_target |>
  mutate(amp_score = case_when(is_congruent == FALSE ~ 0,
                               is_congruent == TRUE ~ 1))|>
  group_by(subject) |>
  count(amp_score)

data_amp_score_percentage <- data_amp_with_amp_score |>
  mutate(amp_score_percentage = case_when(amp_score == 1 ~ 100/72*n))




amp_score_2 <- data_amp_with_amp_score %>%
  group_by(subject) %>%
  summarize(amp_score = mean(is_congruent, na.rm = TRUE))  # Proportion of TRUE in is_congruent column
view(amp_score_2)

data_amp_score_in_percentage <- data_amp_with_amp_score |>
  
  
  


  

100:72 mal n(amp_score =1)
 
  

  
  
  
```


# Self-reports

```{r}

# trial level data
data_selfreport_trial_level <- data_selfreport_raw |>
  select(subject, trialcode, response) |>
  filter(trialcode %in% c("like", "prefer", "positive")) |>
  rename(item = trialcode) |>
  filter(response != "Ctrl+'B'") |>
  mutate(response = as.numeric(response))

# mean scored
data_selfreport_mean_score <- data_selfreport_trial_level |>
  group_by(subject) |>
  summarize(mean_evaluation = mean(response, na.rm = TRUE))

# combined
data_selfreport_scored <- 
  full_join(data_selfreport_trial_level |>
              pivot_wider(names_from = "item",
                          values_from = "response"),
            data_selfreport_mean_score,
            by = "subject")

```

# Affect Misattribution Procedure

TODO extract evaluations on the AMP test blocks and convert to an overall bias score

```{r}


```

# Combine

```{r}

# combine all dfs created in the previous chunks
data_processed_temp <- dat_age_gender |>
  full_join(data_selfreport_scored, by = "subject") |> 
  full_join(data_amp_performance_criteria, by = "subject") |>
  full_join(data_amp_completeness, by = "subject")

# flag all subjects with more than one row in the wide-format data. these should be excluded in the analysis.
# a more elaborate approach would be to track down the individual dupicate cases and determine which of the mulitiple cases should be retained. 
data_processed_duplicates <- data_processed_temp |>
  count(subject) |>
  mutate(exclude_duplicate_data = if_else(n > 1, "exclude", "include")) |>
  select(-n)

# join in the duplicates df
data_processed_before_exclusions <- data_processed_temp |>
  full_join(data_processed_duplicates, by = "subject")

```

# Define master exclusions

```{r}

# create a master exclude_participant variable
data_processed <- data_processed_before_exclusions |>
  mutate(exclude_participant = case_when(tolower(age) == "test" ~ "exclude",
                                         tolower(gender) == "test" ~ "exclude",
                                         is.na(mean_evaluation) ~ "exclude",
                                         # in this case we will exclude participants with missing demographics data or outcomes measures data. 
                                         # Note that "list-wise exclusions" like this aren't always justified, as missingness often isn't at random. 
                                         # How to treat missing data is a  whole area of work in itself, which we wont cover here.
                                         is.na(age) ~ "exclude", 
                                         is.na(gender) ~ "exclude",
                                         exclude_amp_performance == "exclude" ~ "exclude",
                                         exclude_duplicate_data == "exclude" ~ "exclude",
                                         exclude_amp_completeness == "exclude" ~ "exclude", 
                                         TRUE ~ "include"))

```

# Write to disk

```{r}

# in case this dir doesn't exist, create it
dir.create("../data/processed/")

# save data to disk in that dir
write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


